---
title: "Question2"
author: "Niloo sokhandan"
date: "Oct 5, 2018"
output: word_document
---

# Question: Is a user that must call-in to cancel more likely to generate at least 1 addition REBILL?

*Loading the required libraries:*
```{r}
library(readr)
library(dplyr)
library(BSDA)
```

*Loading saved "data.RData" data frame*
```{r}
load("data.RData")
```

*Importing testSamples.CSV file and store it as tS*
```{r}
tS <- read_csv("testSamples.csv")
```

*Grouping data by sample_id (each sample_id appears only once)*
```{r}
data_grouped=summarise(group_by(data, sample_id, transaction_type, test_group))
```

*Creating a table to fill with the results of the probability to generate at least 1 addition REBILL in test group and control group*

#Table 1
```{r echo=FALSE}
Summary_Question2=summarise(group_by(data_grouped),                          P_test_group=100*sum(data_grouped$transaction_type=="REBILL" & data_grouped$test_group==1)/nrow(data_grouped),   
P_control_group=100*sum(data_grouped$transaction_type=="REBILL" & data_grouped$test_group==0)/nrow(data_grouped)) 
library(knitr)
kable(Summary_Question2)
```

*Printing the result*
```{r echo=FALSE}
ifelse(Summary_Question2$P_test_group>Summary_Question2$P_control_group, "The answer to Question 2 is YES","The answer to Question 2 is NO")
```

#Calculating the statisticl significancy of the results

*Keeping columns 1, 4 and 5 of the "data" data frame and removing the rest*
```{r}
data=data[c(1,4,5)]
```
*Calculating the totla amount transacted per user in each test groups*
```{r}
DATA=aggregate(data$transaction_amount, by=list(sample_id=data$sample_id),  FUN=sum)
```
*Renaming the 2nd column of DATA data frame*
```{r}
colnames(DATA)[2] <- "transaction_amount"
```
*Joining DATA data frame to tS data frame by commun field (sample_id)*
```{r}
DATA=merge(x = DATA, y = tS, by = "sample_id", all.x = TRUE)
```
*Extracting data for Control group*
```{r}
Ctrl=subset(DATA, test_group==0)
```
*Extracting data for test group*
```{r}
Test=subset(DATA, test_group==1)
```
*Z.test to calculate the statistical significance level of the results*

# Table 2
```{r}
z.test(Ctrl$transaction_amount, y = Test$transaction_amount, alternative = "greater", mu = 0, sigma.x = sd(Ctrl$transaction_amount),
       sigma.y = sd(Test$transaction_amount), conf.level = 0.95)
```

# Insight:
* Based on table 1, the probability to generate at least 1 addition REBILL is 57% for users cancelling over the phone and 34.5% for users cancelling over the website. so encouraging the users to cancel over the phone increase the chance of rebilling them.
* The results of table 2 shows that we are 95% certain that the claim above is true and valid. 