---
title: "Question3"
author: "Niloo sokhandan"
date: "Oct 5, 2018"
output: word_document
---

# Question: Is a user that must call-in to cancel more likely to generate more revenues?

*Loading the required libraries:*
```{r}
library(readr)
library(dplyr)
library(BSDA)
```

*Loading saved "data.RData" data frame*
```{r}
load("data.RData")
```

*Grouping data by sample_id (each sample_id appears only once)*
```{r}
data_grouped=summarise(group_by(data, sample_id, transaction_type, test_group))
```

*Grouping the transactions per sample_id*
```{r}
trans_sample_id=summarise(group_by(data, sample_id, transaction_amount, test_group))
```
*Extracting the revenue transaction information*
```{r}
Revenue=subset(trans_sample_id, transaction_amount<0)
```

*Creating a table to fill with the results of the mean revenue transaction amount per user in test group and control group*

#Table 1
```{r echo=FALSE}
Summary_Question3=summarise(group_by(Revenue),
          mean_transaction_test_group=mean((subset(Revenue, test_group==1))$transaction_amount), 
          mean_transaction_control_group=mean(subset(Revenue, test_group==0)$transaction_amount))
library(knitr)
kable(Summary_Question3)
```

*Printing the summary result*
```{r}
ifelse(Summary_Question3$mean_transaction_test_group>Summary_Question3$mean_transaction_control_group, "The answer to Question 3 is YES","The answer to Question 3 is NO")
```

*Calculating the statisticl significancy of the results*

*Extracting Revenue data frame for Control group*
```{r}
Ctrl=subset(Revenue, test_group==0)
```
*Extracting Revenue data for test group*
```{r}
Test=subset(Revenue, test_group==1)
```

*Z.test to calculate the statistical significance level of the results*

#Table 2
```{r echo=FALSE}
z.test(Ctrl$transaction_amount, y = Test$transaction_amount, alternative = "greater", mu = 0, sigma.x = sd(Ctrl$transaction_amount),
       sigma.y = sd(Test$transaction_amount), conf.level = 0.95)
```

# Insight:
* Based on table 1, the mean revenue transaction amount per user is 31.2$ for users cancelling over the phone and 25.5$ for users cancelling on the website. As a result, encouraging the users to cancel over the phone  reduce the revenue of the company (Please note that the number of the users cancelling by phone call is lower thn the number of users cancelling through the website, so the clain above is only applicable for this test).
* The results of table 2 shows that we are 95% certain that the above claim is true and valid. 