---
title: "Question4"
author: "Niloo sokhandan"
date: "Oct 5, 2018"
output: word_document
---

# Question: Is a user that must call-in more likely to produce a higher chargeback rate(CHARGEBACKs/REBILLs)?

*Loading the required libraries:*
```{r}
library(readr)
library(dplyr)
library(BSDA)
```

*Loading saved "data.RData" data frame*
```{r}
load("data.RData")
```

*Grouping data by sample_id (each sample_id appears only once)*
```{r}
data_grouped=summarise(group_by(data, sample_id, transaction_type, test_group))
```
#Summarising the data from data_grouped data frame to present:

* The number of rebill cases in test group
* The number of chargeback cases in test group
* The chargeback/rebill ratio in test group
* The number of rebill cases in control group
* The number of chargeback cases in control group
* The chargeback/rebill ratio in control group

#Table 1
```{r echo=FALSE}
Summary_Question4=summarise(group_by(data),
            Nbr_REBILL_test_group        =nrow(data_grouped[(data_grouped$transaction_type=="REBILL") & (data_grouped$test_group==1),]),         
            Nbr_CHARGEBACK_test_group    =nrow(data_grouped[(data_grouped$transaction_type=="CHARGEBACK") & (data_grouped$test_group==1),]),     
            RATIO_test_group             =Nbr_CHARGEBACK_test_group/Nbr_REBILL_test_group,                        
            Nbr_REBILL_control_group     =nrow(data_grouped[(data_grouped$transaction_type=="REBILL") & (data_grouped$test_group==0),]),
            Nbr_CHARGEBACK_control_group =nrow(data_grouped[(data_grouped$transaction_type=="CHARGEBACK") & (data_grouped$test_group==0),]),     
            RATIO_control_group          =Nbr_CHARGEBACK_control_group/Nbr_REBILL_control_group)
library(knitr)
kable(Summary_Question4)
```

*Printing the result:*
```{r echo=FALSE}
ifelse(Summary_Question4$RATIO_test_group>Summary_Question4$RATIO_control_group, "The answer to Question 4 is YES","The answer to Question 4 is NO")
```

#Insight:
*The results of table 1 shows that user that must call-in is more likely to produce a lower chargeback rate (CHARGEBACKs/REBILLs) copmared to a user that cancel through the website, which means that user that must call-in is more likely to get rebilled that charged back.