---
title: "Question1"
author: "Niloo sokhandan"
date: "Oct 5, 2018"
output: word_document
---
# Question: What is the approximate probability distribution between the test group and the control group

*Loading the required libraries:*
```{r}
library(dplyr)
library(readr)
library(ggplot2)
library(BSDA)
```

*Importing testSamples.CSV file and store it as tS:*
```{r}
tS <- read_csv("testSamples.csv")
```
*Importing transData.CSV file and store it as tD:*
```{r}
tD <- read_csv("transData.csv")
```
**Cleaning data :**
*Replacing probable negative transaction amount values for REBILL by NA:*
```{r}
tD[tD$transaction_type=="REBILL" & tD$transaction_amount <0]<- NA
```
*Replacing probable positive transaction amount values for REFUND and ECHARGABLE by NA:*
```{r}
tD[tD$transaction_type!="REBILL" & tD$transaction_amount >0]<- NA
```
*Removing Not Avaialble (NA) data :*
```{r}
tS=na.omit(tS)
tD=na.omit(tD)
```

*Joining tD data frame to tS data frame by commun field (sample_id):*
```{r}
data=merge(x = tD, y = tS, by = "sample_id", all.x = TRUE)
```

*Saving the data in a data frame named "data.RData":*
```{r}
save(data, file = "data.RData")
```

*Changing the title of the 5th column:*
```{r}
colnames(data)[5] <- "Group"
```
*Recoding the Group field values:*
```{r}
data$Group=recode(data$Group,"0"="Control group","1"="Test group")
```

*Plot 1: Plotting Transcation amount probability distribution for each of the transaction types:*
```{r echo=FALSE}
ThemeMain<-theme(title =element_text(size=9, face='bold'),
                 axis.title.x = element_text(size=9,color='black',face='bold'),
                 axis.title.y = element_text(size=9,color='black',face='bold')
)

library(ggplot2)
plot1<-ggplot(data, aes(x=transaction_amount, fill=Group)) +
  geom_histogram(aes(y=..density..), binwidth=2, position=position_jitter(0.1), alpha=0.4)+
    ggtitle("Transcation amount probability distribution")+
  scale_x_continuous("Transaction amount ($)") + 
  scale_y_continuous("Probability (%)") +
  facet_grid(. ~ transaction_type)+
  ThemeMain
  plot1
```

*Keeping columns 1, 4 and 5 of the "data" data frame and removing the rest*
```{r}
data=data[c(1,4,5)]
```
*Calculating the totla amount transacted per user in each test groups:*
```{r}
DATA=aggregate(data$transaction_amount, by=list(sample_id=data$sample_id),  FUN=sum)
```

*Renaming the 2nd column of DATA data frame:*
```{r}
colnames(DATA)[2] <- "transaction_amount"
```

*Joining DATA data frame to tS data frame by commun field (sample_id):*
```{r}
DATA=merge(x = DATA, y = tS, by = "sample_id", all.x = TRUE)
```

*Renaming the 3rd column of DATA data frame:*
```{r}
colnames(DATA)[3] <- "Group"
```

*Recoding the Group field values:*
```{r}
DATA$Group=recode(DATA$Group,"0"="Control group","1"="Test group")
```

*Plot 2: Plotting the Net Transcation amount probability distribution per user:*
```{r echo=FALSE}
library(ggplot2)
plot2<-ggplot(DATA, aes(x=transaction_amount, fill=Group)) +
  geom_histogram(aes(y=..density..), binwidth=5, position="dodge", alpha=0.7) +
      ggtitle("Net Transcation amount probability distribution per user")+
  scale_x_continuous("Transaction amount ($)") + 
  scale_y_continuous("Probability (%)")+
  ThemeMain
  plot2
```
*Extracting data for Control group*
```{r}
Ctrl=subset(DATA, Group=="Control group")
```
*Extracting data for test group*
```{r}
Test=subset(DATA, Group=="Test group")
```
*Z.test to calculate the statistical significance level of the results*

# Table 1
```{r}
z.test(Ctrl$transaction_amount, y = Test$transaction_amount, alternative = "greater", mu = 0, sigma.x = sd(Ctrl$transaction_amount),
       sigma.y = sd(Test$transaction_amount), conf.level = 0.95)
```

#Insight:
* Based on plot 1, the test group (users only cancelling by calling in) get rebilled for higher amount compared to the control group (users cancelling using a web form); yet users cancelling by calling-in are more probable to get charged back or refunded for higher amount.*
* Plot 2 shows that the net transactions (recharge+rebill+refund) of the users cancelling over the phone is higher compared to the users cancelling on the website for values under 150$, whereas users that cancel over the web form ar more probable to have net transactions higher than 150$.
* The results of table 1 shows that we are 95% certain that the claim above is true and valid. 
